---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
```{css}
body {
  font-family: Arial, sans-serif;
  margin: 20px;
  line-height: 1.6;
  color: #222222;
}

h2 {
  color: #2c3e50;
  margin-top: 30px;
  margin-bottom: 12px;
}

p {
  font-size: 18px;
  margin-bottom: 16px;
}
```
## Tracking my eating habits

This dynamic report tracks my eating habits using observational logging.  
Each response represents one eating event. I recorded when I ate, what type of meal it was, and where I ate.  
The report analyses patterns in eating time, meal type, and eating location.

```{r}
library(tidyverse)
library(lubridate)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRxKzbXJ5MyAWdAmIHP_3NAqlWDe8TikrHdXBiodOFeVk1YlAwF16ZXjKviaO1co1vWh_thUKKBIJTM/pub?output=csv")

latest_data <- logged_data %>%
  rename(
    timestamp = Timestamp,
    hour = `What hour did you eat?`,
    meal = `Which meal type is this?`,
    location = `Where did you eat?`
  )

latest_data$hour_dt <- parse_date_time(
  latest_data$hour,
  orders = "d/m I:M p"
)

latest_data$hour_num <- hour(latest_data$hour_dt)
```

- The data currently contains `r nrow(latest_data)` eating events, showing how many eating events were recorded.

- The average eating hour is `r round(mean(latest_data$hour_num), 1)`, suggesting that most eating happens around the   middle of the day. Approximately early afternoon (around 1–2 PM).

- The latest eating time recorded was hour `r max(latest_data$hour_num)`, indicating that some eating occurs later in   the day.

## Meal type distribution

This bar chart shows how often each meal type was recorded.

```{r}
ggplot(latest_data, aes(x = meal)) +
  geom_bar(fill = "skyblue") +
  labs(
    title = "Meal type distribution",
    x = "Meal type",
    y = "Count"
  )
```

## Eating location distribution

This bar chart shows where eating events happened most often.

```{r}
ggplot(latest_data, aes(x = location)) +
  geom_bar(fill = "orange") +
  labs(
    title = "Eating location distribution",
    x = "Location",
    y = "Count"
  )
```

## Summary

Overall, the data shows patterns in eating habits. The charts indicate that snacks were the most frequent meal type, and that most eating events occurred at home.The average eating time is in the early afternoon (around 1–2 PM).
